The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
little space

Increasing the scale of landcover resolution resulted in decreased proportion of
rare and patchy habitats, and low connectivity of individuals in these habitats.
In winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)b). Layer similarity was generally
stable for forest and open habitats except for a contrasting increase in
similarity for forest and decrease in similarity for open habitats 250 m
landcover resolution (Figure \@ref(fig:lcres)c). Layer similarity was not
possible to calculate between winter and summer forage because, at all landcover
resolutions greater than 30 m, there were no individuals connected in the network
layers. <!-- individuals still used forage but in much lower proportion +
lowered opportunity to associate --> Connective redundancy decreased with
increasing landcover resolution due the decrease in connectivity of individuals
in winter forage habitats, resulting in a multilayer network where neighbours
were less frequently repeated in multiple layers <!-- TODO: I'm having a hard
time understanding this previous sentence --> (Figure\@ref(fig:lcres)d).  These
results indicate the importance of matching landcover resolution to scale of
selection as well as ensuring the landcover product used has a resolution fine
enough to detect relevant landscape features and habitats. <!-- TODO: how? This
isn't clear enough for me to follow yet -->

>>>>

Increasing the scale of landcover resolution resulted in decreased proportion of
rare and patchy habitats, and low connectivity of individuals in these habitats.
In winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)b). Layer similarity was generally
stable for forest and open habitats except for a contrasting increase in
similarity for forest and decrease in similarity for open habitats 250 m
landcover resolution (Figure \@ref(fig:lcres)c). Layer similarity was not
possible to calculate between winter and summer forage because, at all landcover
resolutions greater than 30 m, there were no individuals connected in the network
layers. <!-- individuals still used forage but in much lower proportion +
lowered opportunity to associate --> Connective redundancy decreased with
increasing landcover resolution due the decrease in connectivity of individuals
in winter forage habitats, resulting in a multilayer network where neighbours
were less frequently repeated in multiple layers <!-- TODO: I'm having a hard
time understanding this previous sentence --> (Figure \@ref(fig:lcres)d).  These
results indicate the importance of matching landcover resolution to scale of
selection as well as ensuring the landcover product used has a resolution fine
enough to detect relevant landscape features and habitats. <!-- TODO: how? This
isn't clear enough for me to follow yet -->
